---
title: "NLP_Tweet_Engagement_1DCNN"
author: "Christopher Chen"
date: "2024-05-10"
output: html_document
---

#https://www.kaggle.com/code/frankmollard/nlp-basics-tutorial/notebook
```{r }
library(data.table)
library(tm)
library(ggplot2)
library(ggwordcloud)
library(keras)
library(tensorflow)
library(plotly)
library(htmlwidgets)
library(textclean)
library(readr)
library(tidyverse)
#library(qdap)
library(DT)
library(IRdisplay)
library(dichromat)
library(reticulate)
# import("sys", convert = TRUE)$path
library(gridExtra)
library(lubridate)
library(tfruns)
library(tictoc)
#RETICULATE_PYTHON ="C:/Users/chris/AppData/Local/Microsoft/WindowsApps/"
#RETICULATE_PYTHON="C:/Users/chris/miniconda3/python.exe"
```

#Ensure reproducibility
```{r }
#use_session_with_seed(seed = 42, disable_gpu = FALSE, disable_parallel_cpu = FALSE)
set.seed(123)

tensorflow <- import("tensorflow")
tensorflow$random$set_seed(123) 
# Set the environment variable
#Sys.setenv(TF_ENABLE_ONEDNN_OPTS = "1")
```
In the above code, I’ve used the reticulate library to interface with Python from R. The Sys.setenv() function is used to set the TF_ENABLE_ONEDNN_OPTS environment variable to "1". This enables the oneDNN optimizations.

#HyperParameters
```{r }
Learning_Rate = .01
#dec = .00001
#beta_2 = .95
batch_size = 16
eps = 30
inputShape = 40

filter_size = 8
kernel_size = 8
output_dim_size = 8
dropout_rate = 0.35
L1_reg_rate = 0.01
L2_reg_rate = 0.01
```

```{r }
dir <- "C:/Users/chris/Documents/Projects/GitHub R/SOA PA - Hackathon - 20230324/"

train <- read_csv(paste0(dir,"expert_training_original.csv"))

test <- read_csv(paste0(dir,"expert_testing_Original.csv"))

solution <- read_csv(paste0(dir,"expert_solution.csv"))
```

#Data prep
```{r }
emojis <- c("\U0001F600-\U0001F64F", "\U0001F300-\U0001F5FF", "\U0001F680-\U0001F6FF", "\U0001F1E0-\U0001F1FF", "\U00002702-\U000027B0", "\U000024C2-\U0001F251")
```

```{r }
contractions_1 = c( 
"ain't",
"aren't",
"can't",
"can't've",
"'cause",
"could've",
"couldn't",
"couldn't've",
"didn't",
"doesn't",
"don't",
"hadn't",
"hadn't've",
"hasn't",
"haven't",
"he'd",
"he'd've",
"he'll",
"he'll've",
"he's",
"how'd",
"how'd'y",
"how'll",
"how's",
"I'd",
"I'd've",
"I'll",
"I'll've",
"I'm",
"I've",
"isn't",
"it'd",
"it'd've",
"it'll",
"it'll've",
"it's",
"let's",
"ma'am",
"mayn't",
"might've",
"mightn't",
"mightn't've",
"must've",
"mustn't",
"mustn't've",
"needn't",
"needn't've",
"o'clock",
"oughtn't",
"oughtn't've",
"shan't",
"sha'n't",
"shan't've",
"she'd",
"she'd've",
"she'll",
"she'll've",
"she's",
"should've",
"shouldn't",
"shouldn't've",
"so've",
"so's",
"that'd",
"that'd've",
"that's",
"there'd",
"there'd've",
"there's",
"they'd",
"they'd've",
"they'll",
"they'll've",
"they're",
"they've",
"to've",
"wasn't",
"we'd",
"we'd've",
"we'll",
"we'll've",
"we're",
"we've",
"weren't",
"what'll",
"what'll've",
"what're",
"what's",
"what've",
"when's",
"when've",
"where'd",
"where's",
"where've",
"who'll",
"who'll've",
"who's",
"who've",
"why's",
"why've",
"will've",
"won't",
"won't've",
"would've",
"wouldn't",
"wouldn't've",
"y'all",
"y'all'd",
"y'all'd've",
"y'all're",
"y'all've",
"you'd",
"you'd've",
"you'll",
"you'll've",
"you're",
"you've"
)

contractions_2 = c( 
"am not",
"are not",
"cannot",
"cannot have",
"because",
"could have",
"could not",
"could not have",
"did not",
"does not",
"do not",
"had not",
"had not have",
"has not",
"have not",
"he would",
"he would have",
"he will",
"he will have",
"he is",
"how did",
"how do you",
"how will",
"how is",
"I would",
"I would have",
"I will",
"I will have",
"I am",
"I have",
"is not",
"it would",
"it would have",
"it will",
"it will have",
"it is",
"let us",
"madam",
"may not",
"might have",
"might not",
"might not have",
"must have",
"must not",
"must not have",
"need not",
"need not have",
"of the clock",
"ought not",
"ought not have",
"shall not",
"shall not",
"shall not have",
"she would",
"she would have",
"she will",
"she will have",
"she is",
"should have",
"should not",
"should not have",
"so have",
"so is",
"that would",
"that would have",
"that is",
"there would",
"there would have",
"there is",
"they would",
"they would have",
"they will",
"they will have",
"they are",
"they have",
"to have",
"was not",
"we would",
"we would have",
"we will",
"we will have",
"we are",
"we have",
"were not",
"what will",
"what will have",
"what are",
"what is",
"what have",
"when is",
"when have",
"where did",
"where is",
"where have",
"who will",
"who will have",
"who is",
"who have",
"why is",
"why have",
"will have",
"will not",
"will not have",
"would have",
"would not",
"would not have",
"you all",
"you all would",
"you all would have",
"you all are",
"you all have",
"you would",
"you would have",
"you will",
"you will have",
"you are",
"you have"
)

contra <- data.frame(contractions_1, contractions_2)
colnames(contra) <- c("contraction", "expanded")
```

```{r }
cleanUp <- function(CORPUS){
    CORPUS <- tm_map(CORPUS, content_transformer(tolower))
    CORPUS <- tm_map(CORPUS, content_transformer(function(x){mgsub(x, pattern = emojis, replacement = "")}))
    CORPUS <- tm_map(CORPUS, content_transformer(function(x){replace_contraction(x, contraction = contra)}))
    CORPUS <- tm_map(CORPUS, content_transformer(removePunctuation), ucp = F)
    CORPUS <- tm_map(CORPUS, content_transformer(removeNumbers))
    CORPUS <- tm_map(CORPUS, removeWords, stopwords("english"))
    CORPUS <- tm_map(CORPUS, stemDocument, language = "english")
    CORPUS <- tm_map(CORPUS, content_transformer(function(x){gsub("\\S*http+\\S*", "", x)}))
    CORPUS <- tm_map(CORPUS, stripWhitespace)
}
rmse <- function(y_pred, y_true){
  y_pred = k_cast(y_pred, dtype="float32")
  y_true = k_cast(y_true, dtype="float32")
  rmse = k_sqrt(k_mean(k_square(y_pred - y_true), axis=-1)) 
  return(rmse)
}
concatenate_fields <- function(df) {
  df$AllFields <- apply(df, 1, paste, collapse = ", ")
  return(df)
}
Calc_RMSE <- function(df_predicted, df_actual){
t <- merge(x=df_predicted, y=df_actual, by.x="tweet_id", by.y="tweet_id")
sqrt(mean((t$engagement_count.x - t$engagement_count.y)^2))
}
# tokenize text
tokenize_fun_tr = function(dataset) {
  c(indices, target, segments) %<-% list(list(),list(),list())
  for ( i in 1:nrow(dataset)) {
    c(indices_tok, segments_tok) %<-%  safe_encode(tokenizer, data[[DATA_COLUMN]][i], 
                                                     max_len=seq_length)
    indices = indices %>% append(list(as.matrix(indices_tok)))
    target = target %>% append(dataset[[LABEL_COLUMN]][i])
    segments = segments %>% append(list(as.matrix(segments_tok)))
  }
  return(list(indices,segments, target))
}
tokenize_fun_ts = function(dataset) {
  c(indices, segments) %<-% list(list(),list())
  for ( i in 1:nrow(dataset)) {
    c(indices_tok, segments_tok) %<-%  safe_encode(tokenizer, data[[DATA_COLUMN]][i], 
                                                     max_len=seq_length)
    indices = indices %>% append(list(as.matrix(indices_tok)))
    segments = segments %>% append(list(as.matrix(segments_tok)))
  }
  return(list(indices,segments))
}
# read data
dt_data_tr = function(dir, rows_to_read){
  data = data.table::fread(dir, nrows=rows_to_read)
  c(x_train, x_segment, y_train) %<-% tokenize_fun_tr(data)
  return(list(x_train, x_segment, y_train))
}
dt_data_ts = function(dir, rows_to_read){
  data = data.table::fread(dir, nrows=rows_to_read)
  c(x_train, x_segment) %<-% tokenize_fun_ts(data)
  return(list(x_train, x_segment))
}

safe_encode <- function(tokenizer, text, max_len) {
  if (is.null(text) || is.na(text)) {
    return(tokenizer$encode("", max_len = max_len))
  }
  tokenizer$encode(as.character(text), max_len = max_len)
}
```

#Feature Engineering 
```{r }

train$AllFields <- paste0(train$full_text, " from ", train$screen_name, " quote status ", train$is_quote_status, " includes media ", train$includes_media, " includes hashtags ", train$hashtags, " with user mentions ", train$user_mentions, " reply by ", train$in_reply_to_screen_name)
test$AllFields <- paste0(test$full_text, " from ", test$screen_name, " quote status ", test$is_quote_status, " includes media ", test$includes_media, " includes hashtags ", test$hashtags, " with user mentions ", test$user_mentions, " reply by ", test$in_reply_to_screen_name)

```

```{r, eval= TRUE }
corpTRAIN <- Corpus(VectorSource(train$AllFields)) %>% cleanUp()
corpTEST <- Corpus(VectorSource(test$AllFields)) %>% cleanUp()
text <- unlist(corpTRAIN)
textTest <- unlist(corpTEST)

text <- as.data.frame(text)
textTest <- as.data.frame(textTest)

text <- text[1:(nrow(text)-1), ]
text <- as.data.frame(text)
#tail(text)

textTest <- textTest[1:(nrow(textTest)-1), ]
textTest <- as.data.frame(textTest)
#tail(textTest)

val <- data.frame(train$engagement_count, text$text)
colnames(val) <- c("target", "text")
#head(val)

##Tokenizer
voc_size <- val$text %>%
                as.character() %>%
                    paste(., collapse = " ") %>%
                        strsplit(., split = " ") %>%
                            unlist() %>%
                                factor() %>%
                                    unique() %>%
                                        length()
tokenizer <- text_tokenizer(num_words = voc_size)
tokenizer %>%  fit_text_tokenizer(val$text)
#tokenizer$word_index %>% head()

text_tr_seqs <- texts_to_sequences(tokenizer, val$text)
text_te_seqs <- texts_to_sequences(tokenizer, textTest$textTest)
#head(text_tr_seqs); head(text_te_seqs)


x_train <- text_tr_seqs %>% pad_sequences(maxlen = inputShape, padding = "post") 
x_test <- text_te_seqs %>% pad_sequences(maxlen = inputShape, padding = "post")
y_train <- val$target
```

#Keras-BERT Pretrained model setup
```{r, eval= FALSE }
pretrained_path = paste0(dir,"/Pretrained_BERT/uncased_L-12_H-768_A-12")

config_path = file.path(pretrained_path, 'bert_config.json')
checkpoint_path = file.path(pretrained_path, 'bert_model.ckpt')
vocab_path = file.path(pretrained_path, 'vocab.txt')
k_bert = import('keras_bert')
token_dict = k_bert$load_vocabulary(vocab_path)
tokenizer = k_bert$Tokenizer(token_dict)

seq_length = 50L
DATA_COLUMN = 'full_text'
LABEL_COLUMN = 'engagement_count'

model = k_bert$load_trained_model_from_checkpoint(
  config_path,
  checkpoint_path,
  training=T,
  trainable=T,
  seq_len=seq_length)

c(x_train,x_tr_segment, y_train) %<-% 
dt_data_tr(paste0(dir,"expert_training_original.csv"), 26800)
x_train = do.call(cbind,x_train) %>% t()
tr_segments = do.call(cbind,x_tr_segment) %>% t()
y_train = do.call(cbind,y_train) %>% t()
x_train = c(list(x_train ),list(tr_segments))

c(x_test,x_ts_segment) %<-% 
dt_data_ts(paste0(dir,"expert_testing_original.csv"), 8950)
x_test = do.call(cbind,x_test) %>% t()
ts_segments = do.call(cbind,x_ts_segment) %>% t()
x_test = c(list(x_test ),list(ts_segments))

```

#Callback Functions
```{r }
#Early stopping
cb_stop <- callback_early_stopping(monitor = 'val_loss', patience = 5)

#CSV Logging
version <- format(Sys.time(), "%Y%m%d%H%M")
cb_csv_log <- callback_csv_logger(paste0("C:/Users/chris/Documents/Projects/GitHub R/SOA PA - Hackathon - 20230324/Log_Dir/log_", version ,".csv"), separator= ",", append = FALSE)

#Learning rate Scheduler
schedule <- function(epoch, lr) {
  if (epoch >= 4) {
    new_lr <- lr * .98
  } else {
    new_lr <- lr * 1
  }
   return(new_lr)
}
cb_scheduler <- callback_learning_rate_scheduler(schedule)


#Tensorboard 
#dir.create("Log_Dir")
log_dir <- "C:/Users/chris/Documents/Projects/GitHub R/SOA PA - Hackathon - 20230324/Log_Dir"
log_files <- list.files(path=paste0(log_dir,"/train/"), pattern ="\\.v2$", full.names = TRUE)
unlink(log_files)
log_files <- list.files(path=paste0(log_dir,"/validation/"), pattern ="\\.v2$", full.names = TRUE)
unlink(log_files)
cb_tensorboard <-
  callback_tensorboard(
      log_dir = log_dir,
      histogram_freq = 1,
      embeddings_freq =  1,
      write_grads = TRUE,
      write_images = TRUE)
tensorboard(log_dir, launch_browser = TRUE)

#Lambda
on_epoch_begin <- function(epoch, logs) {
  print(paste("Beginning epoch", epoch+1))
}

on_epoch_end <- function(epoch, logs) {
  print(paste("Ending epoch", epoch+1, "with logs:"))
  print(logs)
}

# Create the lambda callback
cb_lambda <- callback_lambda(
  on_epoch_begin = on_epoch_begin,
  on_epoch_end = on_epoch_end
)

#Reduce learning rate on plateau
cb_reduce_lr_plateau <- callback_reduce_lr_on_plateau(
  monitor = "val_loss",
  factor = 0.1,
  patience = 10
)

#Custom callback
LossHistory <- R6::R6Class("LossHistory",
  inherit = KerasCallback,
  
  public = list(
    
    losses = NULL,
     
    on_batch_end = function(batch, logs = list()) {
      self$losses <- c(self$losses, logs[["loss"]])
    }
))
cb_history <- LossHistory$new()

callbacks_list <- list(cb_stop, cb_csv_log, cb_tensorboard, cb_reduce_lr_plateau, cb_scheduler, cb_history)
cb_history$losses
```

```{r, eval= TRUE }
INPUT3 <- layer_input(shape = c(inputShape))

OUTPUT3 <- INPUT3 %>%
        layer_embedding(input_dim = voc_size, 
                      output_dim = output_dim_size
                         ) %>%
       layer_dropout(dropout_rate) %>%
      #layer_batch_normalization() %>%
        layer_conv_1d(filters = filter_size, 
                      kernel_size = kernel_size,
                      activation = "relu",
                      kernel_initializer = initializer_lecun_normal(seed = 123)
                      ) %>%
       layer_dropout(dropout_rate) %>%
      #layer_batch_normalization() %>%
        layer_conv_1d(filters = filter_size*2, 
                      kernel_size = kernel_size,
                      activation = "relu",
                      kernel_initializer = initializer_lecun_normal(seed = 123)
                      ) %>%
        layer_flatten() %>%

        layer_dense(units = 1L, activation = "linear")
model3 <- keras_model(list(INPUT3), OUTPUT3)
summary(model3)
```
#USING Pretrained BERT For TOKENIZER
```{r, eval= FALSE}
# Define the inputs
input3_1 <- layer_input(shape = c(inputShape,output_dim_size))
input3_2 <- layer_input(shape = c(inputShape,output_dim_size))
input3 <- list(input3_1,input3_2)

# Define the model for each input
model3_1 <- input3_1  %>%
  layer_embedding(input_dim = voc_size, 
                  output_dim = output_dim_size
                  ) %>%
  layer_dropout(dropout_rate) %>%
  layer_conv_1d(filters = filter_size, 
                kernel_size = kernel_size,
                activation = "relu",
                kernel_initializer = initializer_lecun_normal(seed = 123)
                ) 

model3_2 <- input3_2 %>%
  layer_embedding(input_dim = voc_size, 
                  output_dim = output_dim_size
                  ) %>%
  layer_dropout(dropout_rate) %>%
  layer_conv_1d(filters = filter_size, 
                kernel_size = kernel_size,
                activation = "relu",
                kernel_initializer = initializer_lecun_normal(seed = 123)
                ) 


# Apply a dense layer to the combined outputs
output3 <- layer_concatenate(list(model3_1, model3_2)) %>%
  layer_dense(units = 1, activation = "linear")

# Create the model
model3 <- keras_model(inputs = input3, outputs = output3)
summary(model3)
```


```{r }
opt=optimizer_adamax(learning_rate = Learning_Rate)
#opt=optimizer_rmsprop(learning_rate = Learning_Rate)
model3 %>% keras::compile(
  loss = "mse",
  optimizer = opt,
  metrics = c("mae")
)
```

```{r }
#Validation sets
# train_size <-floor(0.7*nrow(x_train))
# train_indices <- sample(seq_len(nrow(x_train)), size = train_size)
# 
# # Create the x train/validation sets
# x_train_tr <- x_train[train_indices, ]
# x_train_val <- x_train[-train_indices, ]
# 
# y_train_tr <- y_train[train_indices ]
# y_train_val <- y_train[-train_indices ]

```

```{r }
tic()
hist3_v <- model3 %>%
  fit(
    x_train,
    y_train,
    batch_size = batch_size,
    epochs = eps,
    validation_split = 0.3,
    #validation_data = list(x_train_val,  y_train_val),
    callbacks = callbacks_list,
    shuffle = TRUE
  )
#plot(hist3_v)
#summary(hist3_v)
toc()

preds3 <- model3  %>% predict(x_test)
preds3[preds3<0] <- 0
label_test <- test$tweet_id
pred <- data.frame(tweet_id = label_test, engagement_count = (preds3[, 1]))
VAL_RMSE <- round(Calc_RMSE(pred,solution),1)
VAL_RMSE
```

#Retrain
```{r }
eps3 = ifelse(cb_stop$stopped_epoch > 0, cb_stop$stopped_epoch, eps)
eps3
```

```{r }
tic()
hist3 <- model3 %>%
  fit(
    x_train,
    y_train,
    batch_size = batch_size,
    epochs = eps3,
    shuffle = TRUE
  )
toc()
```

```{r }
results3 <- model3 %>% evaluate(x_train, y_train)
preds3 <- model3  %>% predict(x_test)
preds3[preds3<0] <- 0
```

```{r RMSE function}

label_test <- test$tweet_id
pred <- data.frame(tweet_id = label_test, engagement_count = (preds3[,1]))
Calc_RMSE(pred,solution)

RMSE <- floor(Calc_RMSE(pred,solution))
old_file_name <- paste0("C:/Users/chris/Documents/Projects/GitHub R/SOA PA - Hackathon - 20230324/Log_Dir/log_", version ,".csv")
new_file_name  <-paste0("C:/Users/chris/Documents/Projects/GitHub R/SOA PA - Hackathon - 20230324/Log_Dir/log_", version ,"_", RMSE ,"_",VAL_RMSE,".csv")
file.rename(from = old_file_name, to = new_file_name)

``` 

950.0374
945.1001
962.8919
960.0608
952.3684
960.271
978.4411
981.9069
1081.747
1081.63
1083.187
1080.709
1081.247
1088.816
1082.4
1085.784
1085.507
1084.055
1080.947
1080.914
1085.886
1087.419
1087.641
955.2489
948.5508
949.7785
1015.909
951.5192
949.2582
949.138
1003.165
966.6182
954.0457
961.3686
952.6824
956.8363
955.2128
1050.986
954.2624
1014.334
1085.511
946.0575
948.3357
944.7665
950.2282
947.4584
944.3007
986.5974
985.4645
987.1293
988.0619
948.156
947.5478
987.6998
990.3642
947.8342
944.041
944.2072
946.4703
944.5829
1089.256
1087.59
947.3274
947.7634
948.4101
943.2161
950.2678
947.7354
947.4174
943.7682
944.1097
944.901
946.7359
947.1083
945.1516
944.5032
943.8389
943.8854
949.7513
945.7024
948.2074
941.2969
953.5751
950.669
945.0523
946.6463
946.6463
947.1044

#RMSE
Model 1 - 1077.207
Model 2 - 1071.366
Model 3 - 929.9498
Model blend - 1024.552 
(more epochs accuracy improves)

Sub_XGB - 991.0258 (Public 1560.92459   | Private 599.11411)
2nd - 935.1697     (Public 1508.48776   | Private 523.65355)
1st - 918.72901(?) (Public 1493.0535(?) | Private 501.44248)
#===========================================================
#RMSE Diff               | Public Diff        | Private Diff
#2nd - 55.8561           | 52.43683           | 75.46056
#1st - 72.29679(Approx.) | 67.87109(Approx.)  | 97.67163
#===========================================================


```{r, eval=FALSE }
# Save the model weights to a HDF5 file
#save_model_hdf5(model3, "C:/Users/chris/Documents/Projects/GitHub R/SOA PA - Hackathon - 20230324/Saved_Model/model_05152024_rmse937.h5")
hf_dir <- "C:/Users/chris/Documents/Projects/GitHub R/SOA PA - Hackathon - 20230324/Saved_Model/model_05152024_rmse937.h5"
model <- load_model_hdf5(hf_dir)
#summary(model)
x_test_tt <- text_te_seqs %>% pad_sequences(maxlen = 40, padding = "post")
#mode %>% load_model_weights_hdf5(hf_dir)
preds <- model  %>% predict(x_test_tt)
preds[preds < 0] <- 0
pred <- data.frame(tweet_id = test$tweet_id, engagement_count = (preds))
Calc_RMSE(pred,solution)
```

```{r }

```

```{r }

```

```{r }

```

```{r }

```

```{r }

```

```{r }

```

```{r }

```











